Asymptotic Validity of a Fully Sequential Elimination Procedure for Indifference-Zone Ranking and Selection with Tight Bounds on Probability of Correct Selection

### 2015-04-15 paper/paper_version2.tex
4/15/15

\STATE For each $x$, sample alternative $x$ $n_0$ times and set $n_{0x} \leftarrow n_0$.     
Let $W_{0x}$ and $\lambdahat^2_{0x}$ be the sample mean and sample variance respectively of these samples.     Let $t\leftarrow 0$.     
\STATE Let $A \leftarrow \{ 1,\ldots, k\}$, $\upthresh \leftarrow P^*$.
\WHILE{$x\in\mbox{max}_{x\in A} q_{tx}\left(A\right)<P$}
\WHILE{$\mbox{min}_{x\in A} q_{tx}\left(A\right) \le c$}
 \STATE Let $x\in\mbox{arg min}_{x\in A} q_{tx}\left(A\right)$.
    \STATE Let $\upthresh \leftarrow \upthresh/(1-q_{tx}\left(A\right))$.     
\STATE Remove $x$ from $A$.
\ENDWHILE
  \STATE Let $z \in \mbox{arg min}_{x\in A} n_{tx} / \lambdahat^2_{tx}$.     
\STATE For each $x\in A$, let      $n_{t+1,x} = \ceil\left( \lambdahat^2_{tx} (n_{tz} + B_z) / \lambdahat^2_{tz} \right)$.     \STATE For each $x\in A$, if $n_{t+1,x}>n_{tx}$, take $n_{t+1,x}-n_{tx}$ additional samples from alternative $x$.  Let $W_{t+1,x}$ and $\lambdahat^2_{t+1,x}$ be the sample mean and sample variance respectively of all samples from alternative $x$ thus far.    
\STATE Increment $t$.
 \ENDWHILE
  \STATE Select $\xhat \in\mbox{arg max}_{x\in A} Z_{tx} / n_{tx}$ as our estimate of the best.

@@

\vspace{10mm}
This algorithm generalizes the BIZ procedure with known common variance. In that case, we have that$B_1=\cdots=B_k=1$ and $n_{tx}=t$. The algorithm 2 can be generalized to the continuous case (See appendix B and Frazier (2014)). This procedure is a slightly modification of the original BIZ procedure

@@

The BIZ procedure maps $\left(Y_{n_{x}\left(t\right),x}:t\in\mathbb{N},x\in\left\{ 1,\ldots,k\right\} \right)$
to a selection decision, where $Y_{n_{x}\left(t\right),t}$ is the
sum of samples observed by time $t$. In more detail, it works by
transforming $\left(Y_{n_{x}\left(t\right),x}:A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)$
to $\left(q'_{tx}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)$.
This $q'$ process is given by time process with jumps at $t\in\mathbb{N}$,
\[
q'_{tx}\left(A\right)=q'\left(\left(Z_{tx},t:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right)=\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx}}{n_{tx}}\right)\left/\sum_{x'\in A}\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx}}{n_{tx}}\right)\right.
\]
where the variances are fixed. The same distribtuion over selection
decision will result if we apply the same same selection process to
the following time process with jumps at $t\in\left\{ 0,\delta^{2},2\delta^{2},\ldots\right\} =\delta^{2}\mathbb{N}$,
\[
q'_{tx}\left(A\right)=q'\left(\left(Z_{\frac{t}{\delta^{2}}x},\frac{t}{\delta^{2}}:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right).
\]
Later, we can approximate the previous process by the continuous time
process
\begin{eqnarray}
q_{tx}\left(A\right) & = & q\left(\left(Z_{\frac{t}{\delta^{2}}x},\frac{t}{\delta^{2}}:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right)\label{eq:0.001}
\end{eqnarray}
where $t\geq0$ . Later we will show the difference in selection decisions
vanishes as $\delta\rightarrow0$.

@@

We now gain the insight that we were looking for. We will use $\mathcal{C}_{x}\left(\delta,\cdot\right)$
instead of $Z_{\frac{t}{\delta^{2}}x}$ in $\left(1\right)$, which
is the definition of $q_{tx}\left(A\right)$,
\[
q_{tx}\left(A\right)=q'\left(\left(C_{x}\left(\delta,t\right)\frac{\lambda_{x}^{2}}{\delta\lambda_{z}^{2}}+\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(n_{0}+\frac{t}{\delta^{2}}\right)\delta a_{x},\frac{t}{\delta^{2}}:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right),
\]
the previous equation is true beucase 
\[
Z_{\frac{t}{\delta^{2}}x}=C_{x}\left(\delta,t\right)\frac{\lambda_{x}^{2}}{\delta\lambda_{z}^{2}}+\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(n_{0}+\frac{t}{\delta^{2}}\right).
\]

@@

Let $\epsilon>0$, then there exists $\delta>0$ such that if $\left\Vert \left(u,v\right)\right\Vert _{2}<\delta$
and $ $$\left(u:=\left(u_{1},u_{2}\right),v:=\left(v_{1},v_{2}\right)\right)\in A$,
then 
\begin{equation}
\left|\mbox{min}\left(u_{1},u_{2}\right)-\mbox{min}\left(v_{1},v_{2}\right)\right|<\epsilon.\label{eq:1.10}
\end{equation}
Let $M>N$ such that if $n>M$, then
\[
\left\Vert \left(f_{n}\left(t\right),g_{n}\left(t\right)\right)-\left(f\left(t\right),g\left(t\right)\right)\right\Vert _{2}<\delta
\]
for all $t\in\left[0,t^{*}\right]$. Consequently, if $n>M$, by (\ref{eq:1.10}),
\[
\left|\mbox{min}\left(f_{n}\left(t\right),g_{n}\left(t\right)\right)-\mbox{min}\left(f\left(t\right),g\left(t\right)\right)\right|<\epsilon
\]
for all $t\in\left[0,t^{*}\right]$. Since uniform convergence implies
Skorohod convergente, then $\mbox{min}\left(f_{n},g_{n}\right)\rightarrow\mbox{min}\left(f,g\right)$
in $D_{t^{*}}$, and the result follows.

@@

Thus, replacing $\tau$ with $\tau_{m}+\frac{t^{*}}{nN}$,
\[
\mathbb{P}\left\{ T^{*}\leq\tau_{m}+\frac{t^{*}}{nN}+\frac{1}{nN}\mid\mathcal{F}_{\tau_{m}+\frac{t^{*}}{nN}},T^{*}>\tau_{m}+\frac{t^{*}}{nN}\right\} \geq\Phi\left(\frac{\mbox{min}_{x}a_{x}}{N}\frac{x_{0}}{\lambda_{z}}\right)\Phi\left(-a-\frac{\mbox{max}_{x}a_{x}}{N}\frac{x_{0}^{+}}{\lambda_{z}}\right)^{k-1}
\]
Let $\epsilon$ be the quantity on the righ-hand side of this inequality,
then $\epsilon<1$ and it does not depend on $t^{*}$ and $n$.

@@

We have proved the asymptotic validity of the Bayes-inspired Zone
procedure (Frazier 2014) when the variances are known, which is a
new sequential elemination procedure. This algorithm is relevant because
it takes fewer samples than other IZ procedures, especially for problems
with large numbers of alternatives. Even though this proof does not
guarantee that the algorithm will work for any sample, we know that
it will work if the alternatives are not very different, which are
the most difficult cases.

@@

We are going to define the Skorohod topology on $D[0,\infty)$ by
defining a metric on the space. The Skorohod metricric $d_{t}$ on
$D\left[0,t\right]$ for each $t\geq0$ is:
\[
d_{t}\left(\mathcal{X},\mathcal{Y}\right)=\mbox{inf}_{\lambda\in\Lambda_{t}}\left\{ \left\Vert \lambda-I\right\Vert \vee\left\Vert \mathcal{X}-\mathcal{Y}\circ\lambda\right\Vert \right\} 
\]
where $\Lambda_{t}$ is the set of strictly increasing, continuous
mappings of $\left[0,t\right]$ onto itself, and $\left\Vert \cdot\right\Vert $
is the uniform norm, and $I$ is the identity map. Note that uniform
convergence on $\left[0,t\right]$ implies Skorohod convergence.

>>>>

\STATE For each $x$, sample alternative $x$ $n_0$ times and set $n_{0x} \leftarrow n_0$.     
Let $W_{0x}$ and $\lambdahat^2_{0x}$ be the sample mean and sample variance respectively of these samples.     Let $t\leftarrow 0$.Let $z \in \mbox{arg max}_{x\in A} \lambdahat^2_{tx}$.     
\STATE Let $A \leftarrow \{ 1,\ldots, k\}$, $\upthresh \leftarrow P^*$.
\WHILE{$x\in\mbox{max}_{x\in A} q_{tx}\left(A\right)<P$}
\WHILE{$\mbox{min}_{x\in A} q_{tx}\left(A\right) \le c$}
 \STATE Let $x\in\mbox{arg min}_{x\in A} q_{tx}\left(A\right)$.
    \STATE Let $\upthresh \leftarrow \upthresh/(1-q_{tx}\left(A\right))$.     
\STATE Remove $x$ from $A$.
\ENDWHILE    
\STATE For each $x\in A$, let      $n_{t+1,x} = \ceil\left( \lambdahat^2_{tx} (n_{tz} + B_z) / \lambdahat^2_{tz} \right)$.     \STATE For each $x\in A$, if $n_{t+1,x}>n_{tx}$, take $n_{t+1,x}-n_{tx}$ additional samples from alternative $x$.  Let $W_{t+1,x}$ and $\lambdahat^2_{t+1,x}$ be the sample mean and sample variance respectively of all samples from alternative $x$ thus far.    
\STATE Increment $t$.
 \ENDWHILE
  \STATE Select $\xhat \in\mbox{arg max}_{x\in A} Z_{tx} / n_{tx}$ as our estimate of the best.

@@

\vspace{10mm}
This algorithm generalizes the BIZ procedure with known common variance. In that case, we have that$B_1=\cdots=B_k=1$ and $n_{tx}=t$. The algorithm 2 can be generalized to the continuous case (See appendix B and Frazier (2014)). This procedure is a slightly modification of the original BIZ procedure where $z \in \mbox{arg max}_{x\in A} \lambdahat^2_{tx}$, instead of $z \in \mbox{arg min}_{x\in A} n_{tx} / \lambdahat^2_{tx}$.

@@

Any ranking and selection algorithm can be viewed as mapping from
paths of the $k$-dimensional discrete-time random walk $\left(Y_{tx}:t\in\mathbb{N},x\in\left\{ 1,\ldots,k\right\} \right)$
onto selection decisions. The BIZ procedure's mapping from paths onto
selections decisions can be understood as the composition of three
simpler maps.

The first is the mapping from the raw discrete-time random walk $\left(Y_{tx}:t\in\mathbb{N},x\in\left\{ 1,\ldots,k\right\} \right)$
onto a time changed version of this random walk, written as $\left(Z_{tx}:t\in\mathbb{N},x\in\left\{ 1,\ldots,k\right\} \right)$,
where we recall $Z_{tx}=Y_{n_{x}\left(t\right),t}$ is the sum of
the samples from alternative $x$ observed by stage $t$.

The second maps this time-changed random walk through a non-linear
mapping for each $t,x$ and subset $A\subset\left\{ 1,\ldots,k\right\} $,
to obtain $\left(q_{tx}^{'}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)$,
where

\[
q'_{tx}\left(A\right)=\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx}}{n_{tx}}\right)\left/\sum_{x'\in A}\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx}}{n_{tx}}\right)\right.:=q'\left(\left(Z_{tx},t:x\in A\right),\delta,t\right)
\]
where we note that $n_{x}\left(t\right)$ and $\beta_{t}$ are deterministic
in the version of the known-variance BIZ procedure that we consider
here.

The third maps the paths of $\left(q_{tx}^{'}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)$
onto selection decisions. Specifically, this mapping finds the first
time.

The same distribution over selection decision will result if we apply
the same same selection process to the following time process with
jumps at $t\in\left\{ 0,\delta^{2},2\delta^{2},\ldots\right\} =\delta^{2}\mathbb{N}$,
\[
q'_{tx}\left(A\right)=q'\left(\left(Z_{\frac{t}{\delta^{2}}x},\frac{t}{\delta^{2}}:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right).
\]
Later, we can approximate the previous process by the continuous time
process
\begin{eqnarray}
q_{tx}\left(A\right) & = & q\left(\left(Z_{\frac{t}{\delta^{2}}x},\frac{t}{\delta^{2}}:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right)\label{eq:0.001}
\end{eqnarray}
where $t\geq0$ . Then we will show the difference in selection decisions
vanishes as $\delta\rightarrow0$.

@@

We now gain the insight that we were looking for. We will use $\mathcal{C}_{x}\left(\delta,\cdot\right)$
instead of $Z_{\frac{t}{\delta^{2}}x}$ in $\left(1\right)$, which
is the definition of $q_{tx}\left(A\right)$,
\[
q_{tx}\left(A\right)=q'\left(\left(C_{x}\left(\delta,t\right)\frac{\lambda_{x}^{2}}{\delta\lambda_{z}^{2}}+\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(n_{0}+\frac{t}{\delta^{2}}\right)\delta a_{x},\frac{t}{\delta^{2}}:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right),
\]
the previous equation is true because 
\[
Z_{\frac{t}{\delta^{2}}x}=C_{x}\left(\delta,t\right)\frac{\lambda_{x}^{2}}{\delta\lambda_{z}^{2}}+\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(n_{0}+\frac{t}{\delta^{2}}\right).
\]

@@

Let $\epsilon>0$, then there exists $\delta>0$ such that if $\left\Vert \left(u,v\right)\right\Vert _{2}<\delta$
and $ $$\left(u:=\left(u_{1},u_{2}\right),v:=\left(v_{1},v_{2}\right)\right)\in A$,
then 
\begin{equation}
\left|\mbox{min}\left(u_{1},u_{2}\right)-\mbox{min}\left(v_{1},v_{2}\right)\right|<\epsilon.\label{eq:1.10}
\end{equation}
Let $M>N$ such that if $n>M$, then
\[
\left\Vert \left(f_{n}\left(t\right),g_{n}\left(t\right)\right)-\left(f\left(t\right),g\left(t\right)\right)\right\Vert _{2}<\delta
\]
for all $t\in\left[0,t^{*}\right]$. Consequently, if $n>M$, by (\ref{eq:1.10}),
\[
\left|\mbox{min}\left(f_{n}\left(t\right),g_{n}\left(t\right)\right)-\mbox{min}\left(f\left(t\right),g\left(t\right)\right)\right|<\epsilon
\]
for all $t\in\left[0,t^{*}\right]$. Since uniform convergence implies
Skorohod convergence, then $\mbox{min}\left(f_{n},g_{n}\right)\rightarrow\mbox{min}\left(f,g\right)$
in $D_{t^{*}}$, and the result follows.

@@

Thus, replacing $\tau$ with $\tau_{m}+\frac{t^{*}}{nN}$,
\[
\mathbb{P}\left\{ T^{*}\leq\tau_{m}+\frac{t^{*}}{nN}+\frac{1}{nN}\mid\mathcal{F}_{\tau_{m}+\frac{t^{*}}{nN}},T^{*}>\tau_{m}+\frac{t^{*}}{nN}\right\} \geq\Phi\left(\frac{\mbox{min}_{x}a_{x}}{N}\frac{x_{0}}{\lambda_{z}}\right)\Phi\left(-a-\frac{\mbox{max}_{x}a_{x}}{N}\frac{x_{0}^{+}}{\lambda_{z}}\right)^{k-1}
\]
Let $\epsilon$ be the quantity on the right-hand side of this inequality,
then $\epsilon<1$ and it does not depend on $t^{*}$ and $n$.

@@

We have proved the asymptotic validity of the Bayes-inspired Zone
procedure (Frazier 2014) when the variances are known, which is a
new sequential elimination procedure. This algorithm is relevant because
it takes fewer samples than other IZ procedures, especially for problems
with large numbers of alternatives. Even though this proof does not
guarantee that the algorithm will work for any sample, we know that
it will work if the alternatives are not very different, which are
the most difficult cases.

@@

We are going to define the Skorohod topology on $D[0,\infty)$ by
defining a metric on the space. The Skorohod metric $d_{t}$ on $D\left[0,t\right]$
for each $t\geq0$ is:
\[
d_{t}\left(\mathcal{X},\mathcal{Y}\right)=\mbox{inf}_{\lambda\in\Lambda_{t}}\left\{ \left\Vert \lambda-I\right\Vert \vee\left\Vert \mathcal{X}-\mathcal{Y}\circ\lambda\right\Vert \right\} 
\]
where $\Lambda_{t}$ is the set of strictly increasing, continuous
mappings of $\left[0,t\right]$ onto itself, and $\left\Vert \cdot\right\Vert $
is the uniform norm, and $I$ is the identity map. Note that uniform
convergence on $\left[0,t\right]$ implies Skorohod convergence.
